---
title: "Report onSentiment Analysis on two books 'Great Expectation and Treasure Island'"
author: "Registration # 2101142"
date: ""
output: 
  pdf_document:
    fig_height: 3
    fig_width: 5
  html_document:
    fig_height: 3
    fig_width: 5
  word_document:
    fig_height: 3
    fig_width: 5
---

 Loading packages, libraries
```{r, setup, include=FALSE, warning=FALSE}
require(mosaic)   # Load additional packages here 
# Package names
    packages <- c("ggplot2", "tm", "dplyr", "tidyr", "wordcloud", "syuzhet", "reshape2", "knitr",  "scales", "stringr",  "tidyverse",  "SnowballC", "dgof")
    
    # Install packages not yet installed
    installed_packages <- packages %in% rownames(installed.packages())
    if (any(installed_packages == FALSE)) {
      install.packages(packages[!installed_packages])
    }
    
    # Packages loading
    invisible(lapply(packages, library, character.only = TRUE))

    # Cleaning the environment
    
    rm(list=ls())  # remove all environment variable
    
    
    library(dplyr)           # used for data manipulation such as to manipulate, clean and summarize unstructured/structured data
    library(tidytext)        # used in conversion of text to and from tidy formats
    library(stringr)         # contains a cohesive set of functions to manipulate strings i.e str_detect, str_locate_all
    library(tidyr)           # it contains tools for reshaping (pivoting) and hierarchy (nesting and 'unnesting') of a datase.
    library(ggplot2)         # it is used for plotting graphs, data visulaization
    library(ggthemes)        # used for look and feel of graphs, visualization
    library(gutenbergr)      # a library of many texts
    library(tm)              # text mining package used for data wrangling
    library(SnowballC)       # used for stemming of words, i.e changing words to its root elements
    library(textstem)        # tools for Stemming and Lemmatizing Text
    library(wordcloud)       # it helps to analyze text and visualize keywords/text
    library(scales)          # gives tools to override default breaks, labels and transformations etc.

    
    
knitr::opts_chunk$set(
  tidy=FALSE,     # display code as typed
  warning = FALSE, 
  message = FALSE,
  size="small")   # slightly smaller font for code
```


    library(dplyr)           # used for data manipulation such as to manipulate, clean and summarize unstructured/structured data
    library(tidytext)        # used in conversion of text to and from tidy formats
    library(stringr)         # contains a cohesive set of functions to manipulate strings i.e str_detect, str_locate_all
    library(tidyr)           # it contains tools for reshaping (pivoting) and hierarchy (nesting and 'unnesting') of a datase.
    library(ggplot2)         # it is used for plotting graphs, data visulaization
    library(ggthemes)        # used for look and feel of graphs, visualization
    library(gutenbergr)      # a library of many texts
    library(tm)              # text mining package used for data wrangling
    library(SnowballC)       # used for stemming of words, i.e changing words to its root elements
    library(textstem)        # tools for Stemming and Lemmatizing Text
    library(wordcloud)       # it helps to analyze text and visualize keywords/text
    library(scales)          # gives tools to override default breaks, labels and transformations etc.


```{r}
treasure_island  <- gutenberg_download(c(120))  # downloaded by number and assign contents to data frame
    treasure_island 

    treasure_island <- treasure_island[-c(1:110), ]  # skipping first few rows as those are irrelevant 
    
    data(stop_words)  # a reference tibble of stop words in tidy format 
    stop_words
```


```{r}
 treasure_island_tidy <- treasure_island %>%  # unnest i.e. convert to tidy format 
      unnest_tokens(word, text) %>%    #this function will create collection of words and convert text to lower case and one word per row format
      anti_join(stop_words) # removal of stop words which are not relevant to sentiment analysis
    treasure_island_tidy
      
    treasure_island_tidy %>%count(word, sort = TRUE)  # count most common words

```



```{r}
#visualizing most frequent words of treasure island after converting to tidy format
    treasure_island_tidy %>%
      count(word, sort = TRUE) %>%
      filter(n > 100) %>%
      mutate(word = reorder(word, n)) %>%
      ggplot(aes(word, n)) +
      geom_col() +
      xlab(NULL) +
      coord_flip()
    
    # custom words to be removed from text
    custom_stop_words <- bind_rows(tibble(word = c("light", "food","don't", "it's", "you'll", "i'll",  
                    "i'm","hand","hands",  "till", "word", "dr", "you're"),  # to add own extra stop words
                               lexicon = c("custom")), 
                                   stop_words)
    custom_stop_words
   
    treasure_island_tidy <- treasure_island_tidy %>%
      anti_join(custom_stop_words) # removal of custom stop words 
    treasure_island_tidy %>%count(word, sort = TRUE)  # count most frequent words
    
    treasure_island_tidy

```



```{r}
 #visualizing most frequent words of treasure island after removing custom words
    treasure_island_tidy %>%
      count(word, sort = TRUE) %>%
      filter(n > 105) %>%
      mutate(word = reorder(word, n)) %>%
      ggplot(aes(word, n)) +
      geom_col() +
      xlab(NULL) +
      coord_flip()
    
    #Exhibiting first 30 words of using Wordclound
    treasure_island_tidy %>%
      anti_join(custom_stop_words) %>%
      count(word) %>%
      with(wordcloud(word, n, max.words = 30))
    
    
    # removing numbers/digits from my code
    treasure_island_tidy <- treasure_island_tidy %>%
      filter(!grepl('[0-9]', word))    #regular expression to remove numbers
    treasure_island_tidy
    
    
    treasure_island_tidy %>%count(word, sort = TRUE)  # count most common words after removing numbers

```



```{r}
great_expectations  <- gutenberg_download(c(1400))  # Downloading great expectations book
    great_expectations
    
    great_expectations_with_Skip_rows <- great_expectations[-c(1:78), ]  # skipping first 78 rows
    
    great_expectations_tidy <- great_expectations_with_Skip_rows %>%  # unnest i.e. convert to tidy format 
      unnest_tokens(word, text) %>%
      anti_join(stop_words) # removal of stop words here
    great_expectations_tidy
   
    great_expectations_tidy <- great_expectations_tidy %>%
      anti_join(custom_stop_words) # removal of custom stop words 
    great_expectations_tidy %>%count(word, sort = TRUE)  # count most frequent/common words
    
    great_expectations_tidy <- great_expectations_tidy %>%
      filter(!grepl('[0-9]', word))    # regular expression to remove numbers
    
    # count most common words after converting to tidy format
    g_e_most_common <- great_expectations_tidy %>%count(word, sort = TRUE)  
    g_e_most_common
    
    remove_reg <- "&amp;|&lt;|&gt;"
   
    custom_regex_cleansing <- great_expectations_with_Skip_rows %>%     # removing special characters 
      mutate(text = str_remove_all(text, remove_reg)) %>%
      unnest_tokens(word, text, token = "sentences") %>%
      filter(!word %in% stop_words$word,
             !word %in% str_remove_all(stop_words$word, "'"),
             str_detect(word, "[a-z]"))
     
     
     great_expectations_tidy %>%count(word, sort = TRUE)  # count most frequent/common words

```



```{r}

     great_expectations_tidy %>%count(word, sort = TRUE)  # count most frequent/common words
     
     # Ploting the most frequent words
     barplot(g_e_most_common[1:10,]$n, las = 2, names.arg = great_expectations_tidy[1:10,]$word,
             col ="lightgreen", main ="Top 10 most frequent words",
             ylab = "Word frequencies")
    
     #Displaying most frequent words using ggplot library
     great_expectations_tidy %>%
       count(word, sort = TRUE) %>%
       filter(n > 200) %>%
       mutate(word = reorder(word, n)) %>%
       ggplot(aes(word, n)) +
       geom_col() +
       xlab(NULL) +
       coord_flip()
    
     
     #Displaying 40 words using wordclound
     great_expectations_tidy %>%
       anti_join(custom_stop_words) %>%
       count(word) %>%
       with(wordcloud(word, n, max.words = 40))

```



```{r}
#Frequency/occurences of words and their counts and grouping words by authors, then finding proportion
     frequency <- bind_rows(mutate(great_expectations_tidy, author = "Charles"),
                            mutate(treasure_island_tidy, author = "Louis")) %>% 
       mutate(word = str_extract(word, "[a-z']+")) %>%
       count(author, word) %>%
       group_by(author) %>%
       mutate(proportion = n / sum(n)) %>% 
       select(-n) %>% 
       spread(author, proportion) %>% 
       gather(author, proportion, 'Charles':'Louis')
     
     frequency %>%        #plotting author and proportion on the basis of frequency
       ggplot(aes(x = author, y = proportion)) +
       geom_boxplot(alpha = 0) +
       geom_jitter(alpha = 0.5,
                   color = "tomato",
                   width = 0.2,
                   height = 0.2)
    
    
     # comparing the word frequencies of two books, Louis and Charles Dickens
     # plotting  frequency and proportion where proportion(a subset of words) > 0.0050
     frequency$word <- factor(frequency$word, 
                              levels=unique(with(frequency, 
                                                 word[order(proportion, word, 
                                                            decreasing = TRUE)])))
     frequency <- frequency[complete.cases(frequency), ]
     
     ggplot(aes(x = reorder(word, proportion), y = proportion, fill = author), 
       data = subset(frequency, proportion > 0.0050)) +
       geom_bar(stat = 'identity', position = position_dodge())+
       coord_flip() +
       ggtitle('Comparing the word frequencies of Louis and Charles Dickens')

```



```{r}
 #Extraction chapters/parts information mostly through regular expressions
    
    Original_great_expectations <- great_expectations %>%
      mutate(linenumber = row_number(),  # add cols with line and chapter 
             chapter = cumsum(str_detect(text, 
                                         regex("^chapter [\\divxlc]",
                                               ignore_case = TRUE))))
    
    tail(Original_great_expectations)  # fetching tail part of the contents/text
    
    # exhibiting chapter numbers for every line of text/words
    # applied head for minimizing the records on pdf file
    head(cumsum(str_detect(Original_great_expectations$text, 
                      regex("^chapter [\\divxlc]", 
                            ignore_case = TRUE))) ) 
    
    
   
    
    table(Original_great_expectations$chapter) # no of lines per chapter and book
    
    greatExp_tidy <- Original_great_expectations %>%  # unnest i.e. convert to tidy format, converting to words
      unnest_tokens(word, text) %>%
      anti_join(custom_stop_words) # removal of custom stop words here
    greatExp_tidy %>%count(word, sort = TRUE) # words in desc order after counting them
    
    GExp_Back_to_untidy <- greatExp_tidy %>%          # converting text to untidy format by grouping them by chapter and line number
      group_by(chapter, linenumber) %>%               # 
      summarize(text = str_c(word, collapse = " ")) %>%   # used str_c function which join multiple strings into a single string.
      ungroup()
    GExp_Back_to_untidy

```



```{r}
#working with regular expression to perform different operations.
    # "^chapter [\\divxlc]" regex to locate chapter headings 
    head(str_detect(great_expectations$text,regex("^chapter [\\divxlc]", ignore_case = TRUE)))     # chapter detection  -> using head for limited rows
    head(great_expectations$text%>%str_subset(regex("^chapter [\\divxlc]",ignore_case = TRUE)))     # using pipes to detect chapters  -> using head for limited rows
    sum(str_detect(great_expectations$text,regex("^chapter [\\divxlc]", ignore_case = TRUE))) # sum of chapters detected
    head(str_subset(great_expectations$text,regex("^chapter [\\divxlc]", ignore_case = TRUE))) #-> using head for limited rows
   
    great_expectations$text%>%str_detect(regex("^chapter [\\divxlc]",ignore_case = TRUE))%>%table
    
     # tables no of lines per chapter and book
    head(table(Original_great_expectations$linenumber,Original_great_expectations$chapter)) 
    great_expectations_tidy$word%>%str_detect(regex("^chapter",ignore_case = TRUE))%>%table # count of chapter word

```



```{r}

      #Exploratory data analysis using tm package
      #tm packages used for exploratory data analysis performed below operations
    
      temp <- great_expectations$text
    
      # using tail to view just tail text as otherwise, it will fill all the pdf file with text  
      tail(gsub(' +',' ',temp) ) 
      tail(str_trim(temp, side = "both"))  #Removing whitespace
      
      text_lower <- tolower(great_expectations$text)    # Convert to lower case
      tail(text_lower)  
      
      tail(gsub('[[:digit:]]+', '', temp))  #Removing numbers
      
      tail(gsub('[[:punct:]]', '', temp))  #Removing punctuations
      
      st_words <- removeWords(temp, stopwords()) #Removing stop words
      tail(st_words)
      
      tail(wordStem(temp))     #Stemming 
      
      tail(lemmatize_words(temp))  #Lemmatization

```



```{r}
 # working with sentences and sections
     # splitting text into sentences, lines, using regular expressions
    
          sentences_from_treasure_island <- tibble(text = treasure_island$text) %>% 
            unnest_tokens(sentence, text, token = "sentences")
          
          tibble(text = treasure_island$text) %>% 
            unnest_tokens(line, text, token = "lines")
    
          tibble(text = treasure_island$text) %>%
            unnest_tokens(chapter, text, token = "regex", pattern = "^chapter")
          
          tibble(text = treasure_island$text) %>% 
            unnest_tokens(character, text, token = "characters")
          
          tibble(text = treasure_island$text) %>%
            unnest_tokens(chapter, text, token = "regex", 
                          pattern = "PART [\\dIVXLC]") %>%
            ungroup()

```


```{r}
      
    # common/frequent words in two chosen books  using inner join 
    common_words <- inner_join(great_expectations_tidy,treasure_island_tidy,by="word")
    common_words%>%count(word, sort = TRUE)  # most common common words
    
    #Displaying 50 common words of two books using wordclound
    common_words %>%
      anti_join(custom_stop_words) %>%
      count(word) %>%
      with(wordcloud(word, n, max.words = 50))
    
    # using antijoin to find the words exclusive to each book
    uncommon_words1 <- anti_join(great_expectations_tidy,treasure_island_tidy,by="word")
    uncommon_Great_Expectations <-  uncommon_words1%>%count(word, sort = TRUE)
    uncommon_Great_Expectations  # words not in the Treasure Island book
    
    uncommon_words2 <- anti_join(treasure_island_tidy,great_expectations_tidy,by="word")
    uncommon_Treasure <- uncommon_words2%>%count(word, sort = TRUE)
    uncommon_Treasure  # words not in the Great Expectations book
    
    
    # treasure island words with afinn sentiment dictionary
    get_sentiments("afinn")  # sentiment reference
    exc_treasure_words <- uncommon_Treasure %>%inner_join(get_sentiments("afinn"),"word")
    exc_treasure_words
    
    exc_treasure_words <- exc_treasure_words%>%mutate(weighted=n*value)
    exc_treasure_words  # calc total sentiment contribution of each word
    str(exc_treasure_words) # note 86 words exc to other book 
    exc_treasure_sentiments <- as.numeric(exc_treasure_words$weighted)
    
    hist(exc_treasure_sentiments)  # distribution of the treasure island exc word sentiments 

```


```{r}
 # the following does exactly as above for the Great Expectations book
    # first afinn sentiment is joined with uncommon great expectation words then words are assigned weights
    # and distribution can be checked using histogram chart
    get_sentiments("afinn")  # sentiment reference
    exc_great_expectations_words <- uncommon_Great_Expectations %>%inner_join(get_sentiments("afinn"),"word")
    exc_great_expectations_words <- exc_great_expectations_words%>%mutate(weighted=n*value)
    exc_great_expectations_words
    str(exc_great_expectations_words)
    exc_great_expectations_sentiments <- as.numeric(exc_great_expectations_words$weighted)
    hist(exc_great_expectations_sentiments) # distribution of the Great Expectations exc word sentiments 
    
    # t test difference of means test for the two distributions 
    t.test(exc_great_expectations_sentiments,exc_treasure_sentiments) 
    
    library("dgof")  # looking at the culmulative distributions 
    cul_exc_great_exp_sentiments <- ecdf(exc_great_expectations_sentiments) 
    plot(cul_exc_great_exp_sentiments,main="Culmulative plots",pch = c(17),ylab="",xlab="sentiment")
    cul_exc_treasure_sentiments <- ecdf(exc_treasure_sentiments) # CDF for Treasure values
    lines(cul_exc_treasure_sentiments,col="red",pch = c(19)) # combine in one plot 
    abline(v=mean(exc_treasure_sentiments), col="blue") # vertical line  at Treasure mean 
    legend("bottomleft", 
           legend = c("Great Expectations","Treasure Island"), 
           col = c("black","red"), 
           pch = c(17,19), 
           bty = "n", 
           pt.cex = 2, 
           cex = 1.2, 
           text.col = "black", 
           horiz = F , 
           inset = c(0.1, 0.1)) # legend added to plot
    
    
    
    # kolmogorov-smirnov test for a difference in distributions
    # kolmogorov-smirnov test(kst) compares the commulative distribution of two given sets.
    # basically it presents the max difference between the comulative distributions
    # it calculates the P value and samples sizes
    # Kst has max value 1 and min 0, max value describes the best fit of the data
    # while the min value shows the fit is not significant
    ks.test(exc_treasure_sentiments,cul_exc_great_exp_sentiments) # p value is sig 
    # very low p value shows that the distributions differ 

```



```{r}
 
    # The below line of code performs the following operations
    # sentiments dictionaries afinn, bing and nrc get loaded
    # then sentiment related to nrc are tested for joy sentiment words,
    # which gives information about the joy sentiment, their frequencies
    # similary sentiments of two books have been examined on the basis of different sentiment references
    
    
    #different sentiments dictionaries
    get_sentiments("afinn")  # sentiment reference
    get_sentiments("bing")
    get_sentiments("nrc")
    
    
    nrc_joy <- get_sentiments("nrc") %>% 
      filter(sentiment == "joy")  # select joy sentiment words
    nrc_joy         # result        A tibble: 687 x 2
    
    
    great_expectations_tidy_sentiment_joy <- great_expectations_tidy %>%
      inner_join(nrc_joy)   # joy words in great expectations
    
    great_expectations_tidy_sentiment_joy
    
    #Displaying first 20 words of Great expectations using wordclound
    great_expectations_tidy_sentiment_joy %>%
      anti_join(custom_stop_words) %>%
      count(word) %>%
      with(wordcloud(word, n, max.words = 20))
    
    great_expectations_tidy_sentiment_joy %>%
      inner_join(nrc_joy) %>%
      count(word, sort = TRUE)  # most popular joy words
  
    
    ge_bing_sentiment <- great_expectations_tidy %>%
      inner_join(get_sentiments("bing"),"word")
    ge_bing_sentiment
    
    #  sentiment is described with bing dictionary and in the below scenario,
    #  words list have been chosen and sentiment difference is found out
    #  sentiment described below is positive sentiment difference negative sentiment words. 
    ge_bing_sentiment <- great_expectations_tidy %>%  
      inner_join(get_sentiments("bing")) %>%
      count(gutenberg_id, index = row_number() %/% 70, sentiment)%>%     # count pos/neg over 70 words
      pivot_wider(names_from = sentiment, values_from = n, values_fill = 0) %>% 
      mutate(sentiment = positive - negative)
    ge_bing_sentiment

```


```{r}
# visualization of sentiments difference in ggplot
    # mostly the bing lexican sentiments are negative in great expectations
    ggplot(ge_bing_sentiment, aes(index, sentiment, fill = gutenberg_id )) +     
      geom_col(show.legend = FALSE) +
      facet_wrap(~gutenberg_id , ncol = 2, scales = "free_x")
    
   
    treasure_island_tidy_sentiment_joy <- treasure_island_tidy %>%
      inner_join(nrc_joy)   # joy words in treasure Island
    
    treasure_island_tidy_sentiment_joy
    
    #Displaying first 20 words of treasure island using wordclound
    treasure_island_tidy_sentiment_joy %>%
      anti_join(custom_stop_words) %>%
      count(word) %>%
      with(wordcloud(word, n, max.words = 20))
    
    treasure_island_tidy_sentiment_joy %>%
      inner_join(nrc_joy) %>%
      count(word, sort = TRUE)  # most popular joy words
    
    
    te_bing_sentiment <- treasure_island_tidy %>%
      inner_join(get_sentiments("bing"),"word")
    te_bing_sentiment
    
    #  sentiment is described with bing dictionary and in the below scenario,
    #  words list have been chosen and sentiment difference is found out
    #  sentiment described below is positive sentiment difference negative sentiment words. 
    te_bing_sentiment <- treasure_island_tidy %>%  
      inner_join(get_sentiments("bing")) %>%
      count(gutenberg_id, index = row_number() %/% 70, sentiment)%>%     # count pos/neg over 70 words
      pivot_wider(names_from = sentiment, values_from = n, values_fill = 0) %>% 
      mutate(sentiment = positive - negative)
    te_bing_sentiment
    
    # visualization of sentiments difference in ggplot
    ggplot(te_bing_sentiment, aes(index, sentiment, fill = gutenberg_id )) +     
      geom_col(show.legend = FALSE) +
      facet_wrap(~gutenberg_id , ncol = 2, scales = "free_x")
    
    # For both books bing lexicon sentiments are almost negative

```


```{r}
 
    treasure_island_bigrams <- tibble(text = treasure_island$text) %>% 
      unnest_tokens(bigram, text, token = "ngrams", n = 2)  # using the bigram option 
    treasure_island_bigrams
    
    treasure_island_bigrams %>%count(bigram, sort = TRUE) # most popular bigrams are stop word pairs
    
   
    
    bigrams_separated <- treasure_island_bigrams %>%
      separate(bigram, c("word1", "word2"), sep = " ") # separates the bigram in 2 cols
    bigrams_separated
    
    bigrams_filtered <- bigrams_separated %>%
      filter(!word1 %in% stop_words$word) %>%  # removes via single stop words
      filter(!word2 %in% stop_words$word)
    bigrams_filtered
    
    # new bigram counts:
    bigram_counts <- bigrams_filtered %>%count(word1, word2, sort = TRUE)
    bigram_counts
    
    bigrams_united <- bigrams_filtered %>%
      unite(bigram, word1, word2, sep = " ")
    bigrams_united  # can be used to recombine into a bigram
    
    bigrams_separated %>%
      filter(word1 == "not") %>%  # count cases of negation , changing the sentiment
      count(word1, word2, sort = TRUE)
    
    AFINN <- get_sentiments("afinn")
    AFINN
    
    not_words <- bigrams_separated %>%
      filter(word1 == "not") %>%
      inner_join(AFINN, by = c(word2 = "word")) %>%
      count(word2, value, sort = TRUE)
    not_words
    
    not_words %>%
      mutate(contribution = n * value) %>%  # these sentiments are faulty
      arrange(desc(abs(contribution))) %>%
      head(20)

```


```{r}
not_words %>%
      mutate(contribution = n * value) %>%
      arrange(desc(abs(contribution))) %>%
      head(20) %>%
      mutate(word2 = reorder(word2, contribution)) %>%  # can pipe above to ggplot
      ggplot(aes(n * value, word2, fill = n * value > 0)) +
      geom_col(show.legend = FALSE) +
      labs(x = "Sentiment value * number of occurrences",
           y = "Words preceded by \"not\"")
    
    negation_words <- c("not", "no", "never", "without") # more negation words
    
    negated_words <- bigrams_separated %>%
      filter(word1 %in% negation_words) %>%  # filter for the set of negation words
      inner_join(AFINN, by = c(word2 = "word")) %>%
      count(word1, word2, value, sort = TRUE)
    boxplot(negated_words$value)  
    # The box plot is suggesting that most of the bigrams are positive when 
    # first word is in negation words. 
    
    
    treasure_and_great_expectations <- gutenberg_download(c(120, 1400))
    
    tidy_treasure_and_great_expectations <- treasure_and_great_expectations %>%
      unnest_tokens(word, text) %>%
      anti_join(stop_words)
    tidy_treasure_and_great_expectations %>%  count(word, sort = TRUE)
    
  
    
    bind_rows(mutate(great_expectations_tidy, author = "A"), # binding by rows produces NAs
              mutate(treasure_island_tidy, author = "B")) %>% 
      mutate(word = str_extract(word, "[a-z']+")) %>% 
      count(author, word) %>%
      group_by(author) %>%
      mutate(proportion = n / sum(n))%>%  # the values are proportions of word per author
      select(-n)%>% 
      pivot_wider(names_from = author, values_from = proportion) # non tidy authors are in the col names 

```



```{r}
 frequency <- bind_rows(mutate(great_expectations_tidy, author = "A"), 
                           mutate(treasure_island_tidy, author = "B")) %>% 
      mutate(word = str_extract(word, "[a-z']+")) %>%
      count(author, word) %>%
      group_by(author) %>%
      mutate(proportion = n / sum(n)) %>% 
      select(-n) %>% 
      pivot_wider(names_from = author, values_from = proportion) %>%
      pivot_longer('A':'B', # addition to the pipe selects two authors
                   names_to = "author", values_to = "proportion")
    
    frequency
    
    
    bingnegative <- get_sentiments("bing") %>%   # list of negative words from the Bing lexicon. 
      filter(sentiment == "negative")
    head(bingnegative)
    table(bingnegative$sentiment) # 4781  negative words
   
    great_expectations_tidy
    bingnegative
    
    great_expectations_tidy %>%semi_join(bingnegative) # negative words in the book
    
    great_expectations_tidy %>%
      semi_join(bingnegative) %>%  # 
      group_by(gutenberg_id, word) %>%
      summarize(negativewords = n())  # count neg words by chapt  and book

```


```{r}

    #analysis of bing, nrc and afinn lexicals
    # It can be observed from the graphs that Afinn and Bing words are more negative
    # NRC words are more positive 
    # The above results are for the book great expectations. 
     afinn <- great_expectations_tidy %>% 
       inner_join(get_sentiments("afinn")) %>% 
       group_by(index = row_number() %/% 100) %>% 
       summarise(sentiment = sum(value)) %>% 
       mutate(method = "AFINN")
     
     bing_and_nrc <- bind_rows(
       great_expectations_tidy %>% 
         inner_join(get_sentiments("bing")) %>%
         mutate(method = "Bing"),
       great_expectations_tidy %>% 
         inner_join(get_sentiments("nrc") %>% 
                      filter(sentiment %in% c("positive", 
                                              "negative"))
         ) %>%
         mutate(method = "NRC")) %>%
       count(method, index = row_number() %/% 100, sentiment) %>%
       pivot_wider(names_from = sentiment,
                   values_from = n,
                   values_fill = 0) %>% 
       mutate(sentiment = positive - negative)
     
     bind_rows(afinn, 
               bing_and_nrc) %>%
       ggplot(aes(index, sentiment, fill = method)) +
       geom_col(show.legend = FALSE) +
       facet_wrap(~method, ncol = 1, scales = "free_y")

```


```{r}
# Calculating positive and negative words for understanding the difference between 3 dictionaries
     
     get_sentiments("nrc") %>% 
       filter(sentiment %in% c("positive", "negative")) %>% 
       count(sentiment)
           #  negative   3318
           #  positive   2308
     
     
     get_sentiments("bing") %>% 
       count(sentiment) # negative lexicons have higher values in bing as compared to NRC 
           #  negative   4781
           #  positive   2005
     
     #counting bing words
     
     bing_word_counts <- great_expectations_tidy %>%
       inner_join(get_sentiments("bing")) %>%
       count(word, sentiment, sort = TRUE) %>%
       ungroup()
     
     bing_word_counts
     
     #Results
     # It is observed that bing has more negative lexicons than nrc
     # Hence we can get more clear picture when using bing lexicon
     
     #contribution to sentiment graph plotting 
     # It can be observed that words are negatively skewed
     bing_word_counts %>%
       group_by(sentiment) %>%
       slice_max(n, n = 10) %>% 
       ungroup() %>%
       mutate(word = reorder(word, n)) %>%
       ggplot(aes(n, word, fill = sentiment)) +
       geom_col(show.legend = FALSE) +
       facet_wrap(~sentiment, scales = "free_y") +
       labs(x = "Contribution to sentiment",
            y = NULL)
     # it can be seen clearly that bing has comparitvely more negative words than positve 

```


```{r}

     #Positive and negative words of both books using bing dictionary
     
     great_expectations_tidy %>%   #positive and negative words of great expectations
       inner_join(get_sentiments("bing")) %>%
       count(word, sentiment, sort = TRUE) %>%
       acast(word ~ sentiment, value.var = "n", fill = 0) %>%
       comparison.cloud(colors = c("gray20", "gray80"),
                        max.words = 100)
     
     treasure_island_tidy %>%  #positive and negative words of treasure Island
       inner_join(get_sentiments("bing")) %>%
       count(word, sentiment, sort = TRUE) %>%
       acast(word ~ sentiment, value.var = "n", fill = 0) %>%
       comparison.cloud(colors = c("gray20", "gray80"),
                        max.words = 100)
    
    
    #---------------------The End--------------------------------------#

```



```{r}


```


```{r}


```


```{r}


```





  